### 2021-03-07 paper.Rmd
paragraph on pp index

@@

interesting, index function, $f: \mathbb{R}^{n \times d} \mapsto \mathbb{R}$, normality, theoretical result: [@Diaconis1984-mv], aslo peter huber projection pursuit

index: 
  - initial idea from Friedman, orthonormal function expansion (Do we need to review these old index contruction?)
  - holes, central mass, PDA, LDA
  - scagnostic indices
  - skewness & kurtosis index loperfido (moment)
  - chi-square @posse for detect spiral

>>>>

[grand/ guided / manual tour or 1D/ 2D display in tourr???]

@@

To define whether a projection is interesting or not in the guided tour, an index function is used. An index function defines a surjection function from the projection $Y$ in $ \mathbb{R}^{n \times d}$ to a scalar in $\mathbb{R}$. For the high-dimensional data, an interesting projection is the one that deviates from normality, as discussed in @Diaconis1984-mv and @Huber1985-zq [expand more here]. Numerous index functions have been developed since the initial index proposed by @Friedman1974-ck: <!-- entropy-based index? --> holes and central mass index [@Cook2008-nl] computes the deviation of the projected data from a normal distribution; @Posse1995-ih proposed a chi-square index for detecting the spiral structure in the data;  kurtosis and skewness indices are raised in @Loperfido2020-xj and @Loperfido2018-ga to detect outliers in financial time series; and most recently, scagnostic indices [@Laa2020-zj] provides eight measures for summarising information between pairs of variables in scatter plot matrices.
